R5R

### 2020-08-22 r-package/tests_marcus/tests r5r.Rmd
Testing cleaner version of travel time matrix.

ttm %>% filter(fromId %in% orig) %>%
  ggplot() +
  geom_point(data=points, aes(x=lon, y=lat), colour="grey85") +
  geom_point(aes(x=toLon, y=toLat, colour=travel_time)) +
  scale_color_distiller(palette = "Spectral") +
  coord_map() +
  facet_wrap(~fromId)
```

>>>>

ttm %>% filter(fromId %in% orig) %>%
  left_join(points, by=c("toId" = "id")) %>%
  ggplot() +
  geom_point(data=points, aes(x=lon, y=lat), colour="grey85") +
  geom_point(aes(x=lon, y=lat, colour=travel_time)) +
  scale_color_distiller(palette = "Spectral") +
  coord_map() +
  facet_wrap(~fromId)
```
